Deciding to Disclose

### 2015-11-13 agent_models.tex
eq 10
FFH acronym

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

@@

\begin{equation}
v(u_{i})=\begin{cases}
f(u_{i}),& \text{if}\, u_{i}>0\\
0,& \text{if}\, u_{i}=0\\
\lambda g(u_{i}),& \text{if}\, x<0
\end{cases},
\end{equation}

>>>>

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

@@

\begin{equation}
v(u_{i})=\begin{cases}
f(u_{i}),& \text{if}\, u_{i}>0\\
0,& \text{if}\, u_{i}=0\\
\lambda g(u_{i}),& \text{if}\, u_{i}<0
\end{cases},
\end{equation}
